---
title: "Analog Reading CM230"
author: "Lucian Pierre"
date: "06/04/2021"
output: 
github_document:
  fig_width: 9
  fig_heigth: 5

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
There are conductivimeters that use digital measures and others that use analog measures for the calculation of water conductivity, the digital ones allow a very approximate measurement by the devices that will be coupled to it for IOT communication, however the analog behind an error of your AD converter, making it difficult the correct reading by this iot device.

  This package is used to calculate the conductivity reading of conductivimeters using the analog base, taking into account a series of readings obtained by sampling, a form of approximation was generated, reducing the error brought by the microcontroller AD. The reading is given in us / cm3 microsimens per cubic centimeter the input must be entered in mv, milli volts, it is also necessary to calibrate the conductivity meter to make its use feasible.
 
 ##Directions for use:
 
  Using a multimeter or the analog pin of the microcontroller, check the voltage that the analog output of the conductivimeter presents, with it in your hands, enter the value in the function and the reading value will be the presented conductivity, the same can be done in the micro controller.
  
  We have:
  Reading <200us / cm3 = drinking water
  Reading> 200us / cm3 = non-drinking water
  



```{r message = FALSE, warning = FALSE}
library(CondutivimetroAnalogico)

```

```{r, eval = FALSE}
CondutivimetroAnalogico::Leitura(a)
```

